Followers Are Not Enough: Beyond Structural Communities in Online Social Networks

### 2014-04-22 paper-for_arxiv/intro.tex
Minor edits to Elisa's additions / revisions.

%A large body of work exists on methods for automatic detection of communities within networks~\cite{newman2004fast,newman2004finding,rosvall2008maps,blondel2008fast,LancichinettiPlos}. See~\cite{fortunato2010community} for a recent review. 
\textcolor{red}{A large body of work exists on methods for automatic detection of communities within networks, among which we recall Girvann and Newman algorithm [32, 33], Infomap [39], Leuven [3], and the recently introduced OSLOM [24].}
All these methods \emph{begin} with a given network, and then attempt to uncover structure present in the network, i.e., they are agnostic to how the network was constructed. As opposed to this agnostic analysis, we propose and illustrate the importance of a question-focused approach. We believe that in order to understand the communities present in a data set, it is important to begin with a clear picture of the community type under consideration, and then perform the network collection and community detection with that community type in mind.

>>>>

%A large body of work exists on methods for automatic detection of communities within networks~\cite{newman2004fast,newman2004finding,rosvall2008maps,blondel2008fast,LancichinettiPlos}. See~\cite{fortunato2010community} for a recent review. 
\textcolor{red}{A large body of work exists on methods for automatic detection of communities within networks, among which we recall the Girvan and Newman algorithm~\cite{newman2004finding}, Infomap~\cite{rosvall2008maps}, Louvain\cite{~blondel2008fast}, and the recently introduced OSLOM\cite{LancichinettiPlos}.}
All these methods \emph{begin} with a given network, and then attempt to uncover structure present in the network, i.e., they are agnostic to how the network was constructed. As opposed to this agnostic analysis, we propose and illustrate the importance of a question-focused approach. We believe that in order to understand the communities present in a data set, it is important to begin with a clear picture of the community type under consideration, and then perform the network collection and community detection with that community type in mind.

### 2014-04-22 paper-for_arxiv/methods.tex
Minor edits to Elisa's additions / revisions.

This last criterion in particular poses a problem because the majority of community detection algorithms developed so far are built to find partitions of a network and few are aimed at finding overlapping communities \cite{BaumesGKMP05,PalEtAl05,ZhaWanZha07,Gre07,PhysRevE.77.016107,Lancichinetti2009,PhysRevE.80.016105,Kovacs2010}. Among these methods, even fewer deal with directed or weighted networks. For example, the work of~\cite{PalEtAl05} on clique percolation can account for both features, but not at the same time. A recent method proposed by~\cite{LancichinettiPlos}, OSLOM (Order Statistics Local Optimization Method), is one of the first methods  able to deal with all of these features simultaneously. Their method relies on a fitness function that measures the statistical significance of clusters with respect to random fluctuations, and attempts to optimize this fitness function across all clusters. 
\textcolor{red}{Following~\cite{Lancichinetti2010}, the significance measure is defined as the probability of finding the cluster in a network without community structure. The null model used is basically the same as the one adopted by Newman and Girvan to define modularity, i.e. it is a model that generates random graphs with a given degree distribution. The authors tested their algorithm on different benchmarks (LFR and Girvan-Newman) and real networks (such as the US air transportation and the word association network), and compared its performance against the best algorithms
currently available (i.e the ones mentioned in the introduction), and found excelent results. Moreover, they showed that OSLOM is also able to recognize the absence, and not simply the presence, of community structure, by testing it on random graphs. This feature of the algorithm plays an important role in the analysis of real data networks, since it is not always the case that a community structure is indeed present and it is therefore useful to be able to detect its absence too. 
Therefore, given its versatily and its performance, in this paper we used OSLOM to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network.}
%For this paper we use OSLOM since it allowed us to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network, and its authors showed that it performs very well on various types of artificial benchmark graphs and also on several real networks.

>>>>

This last criterion in particular poses a problem because the majority of community detection algorithms developed so far are built to find partitions of a network and few are aimed at finding overlapping communities \cite{BaumesGKMP05,PalEtAl05,ZhaWanZha07,Gre07,PhysRevE.77.016107,Lancichinetti2009,PhysRevE.80.016105,Kovacs2010}. Among these methods, even fewer deal with directed or weighted networks. For example, the work of~\cite{PalEtAl05} on clique percolation can account for both features, but not at the same time. A recent method proposed by~\cite{LancichinettiPlos}, OSLOM (Order Statistics Local Optimization Method), is one of the first methods  able to deal with all of these features simultaneously. Their method relies on a fitness function that measures the statistical significance of clusters with respect to random fluctuations, and attempts to optimize this fitness function across all clusters. 
\textcolor{red}{Following~\cite{Lancichinetti2010}, the significance measure is defined as the probability of finding the cluster in a network without community structure. The null model used is basically the same as the one adopted by Newman and Girvan to define modularity, i.e. it is a model that generates random graphs with a given degree distribution. The authors tested their algorithm on different benchmarks (LFR and Girvan-Newman) and real networks (such as the US air transportation and the word association network), and compared its performance against the best algorithms
currently available (i.e the ones mentioned in the introduction), and found excellent results. Moreover, they showed that OSLOM is also able to recognize the absence, and not simply the presence, of community structure, by testing it on random graphs. This feature of the algorithm plays an important role in the analysis of real data networks, since it is not always the case that a community structure is indeed present and it is therefore useful to be able to detect its absence too. 
Therefore, given its versatility and performance with benchmark network, in this paper we used OSLOM to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network.}
%For this paper we use OSLOM since it allowed us to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network, and its authors showed that it performs very well on various types of artificial benchmark graphs and also on several real networks.

### 2014-04-22 paper-for_arxiv/results.tex
Minor edits to Elisa's additions / revisions.

\textcolor{red}{Last but not least, it is interesting noticing that in the top ten most influential users (ranked using the total outgoing strength in the activity-based network) we find two users (Ann Tran and Jessica Northey) that were listed by Forbes in the "Top 10 Social Media Influencers".}

>>>>

\textcolor{red}{Lastly, it is interesting to note that in the top ten most influential users (ranked using the total outgoing strength in the activity-based network) we find two users (Ann Tran and Jessica Northey) that were listed by Forbes in the "Top 10 Social Media Influencers".}
